05_DESeq_manipulation

### 2019-05-13 analysis/05_DESeq2_manipulate.Rmd
removed unused pca stats
tweeks

knitr::opts_chunk$set(fig.path = '../figures/manipulation/',cache=TRUE)

```

@@

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
m.colData <- read.csv("../results/00_colData_manipluation.csv", header = T, row.names = 1)
m.countData <- read.csv("../results/00_countData_manipluation.csv", header = T, row.names = 1)
geneinfo <- read.csv("../results/00_geneinfo.csv", row.names = 1)

# set levels
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("m.inc.d3", "m.inc.d8", "m.inc.d9",
                                "m.inc.d17",  "prolong", "extend", "m.n2"))

@@

pca34 <- ggplot(pcadata, aes(PC3, PC4,color = treatment)) + 
  geom_point(size = 2, alpha = 1) +
  stat_ellipse(type = "t") +
  xlab(paste0("PC3: ", percentVar[3],"% variance")) +
  ylab(paste0("PC4: ", percentVar[4],"% variance")) +
  theme_cowplot(font_size = 8, line_size = 0.25) +
  labs(subtitle = eachgroup)
print(pca34)

summary(aov(PC3 ~ treatment, data=pcadata))

summary(aov(PC4 ~ treatment, data=pcadata))

summary(aov(PC5 ~ treatment, data=pcadata))

summary(aov(PC6 ~ treatment, data=pcadata))

>>>>

knitr::opts_chunk$set(fig.path = '../figures/manipulation/')
```

@@

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
m.colData <- read.csv("../metadata/00_colData_manipluation.csv", header = T, row.names = 1)
m.countData <- read.csv("../results/00_countData_manipluation.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

# set levels
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("m.inc.d3",  "m.inc.d9",
                                "m.inc.d17", "m.inc.d8", "prolong", "extend", "m.n2"))

@@

pca34 <- ggplot(pcadata, aes(PC3, PC4,color = treatment)) + 
  geom_point(size = 2, alpha = 1) +
  stat_ellipse(type = "t") +
  xlab(paste0("PC3: ", percentVar[3],"% variance")) +
  ylab(paste0("PC4: ", percentVar[4],"% variance")) +
  theme_cowplot(font_size = 8, line_size = 0.25) +
  labs(subtitle = eachgroup)
#print(pca34)
